The Elements of Theses

### 2014-09-07 thesis/Background.tex
grammar changes

\section{Deduplication}
\label{back:dedup}
Backup storage for VM snapshots in the cloud contains PBs of data from many VMs,
the data redundancy in such a data set is very high\cite{Jayaram2011, agrawal07}.
If we treat each snapshot as a single data object, the similarities between snapshots
can not be utilized. Therefore we need better method to break files into data blocks.
In the recent decade, data deduplication techniques are emerged to solve this data
redundancy problem in backup systems.
Most of data de-duplication methods can be categorized by their granularity:

@@

\item \textbf{By variable size block:} This method breaks data into variable size blocks, and the block boundary
is only decided by local data content, so it is also called content-based chunking. 
Because of the chunk boundaries are only decided by local data content,
this method is modification-resistant. It resolves the
limitations in the previous two methods, and provides
best de-duplication efficiency. 
\end{itemize}

@@

Policroniades\cite{poli04} gives out
experimental results and present a comparative analysis
to three de-duplication methods: First, the content based chunking
is always the best strategy to discover redundancy in any data sets.
Second, the fixed size block method can sometimes provides
close results compare to content based chunking, and it has smalleris less
computation intensive. Finally, if only for local file system,
file compression is still the
best strategy to save disk space, combining the content based chunking
with compression does not justify the computation it costs.

Data de-duplication is extensively used in saving bandwidth for data synchronization.
The popular rsync\cite{rsync} protocol exploits the similarity of two directory trees
using fixed size blocks de-duplication. 
LBFS uses content-based chunking to improve the NFS protocol, 
it avoids transmitting redundant chunks which already exist at the other side.
But data du-duplication has its cost. Content-based chunking algorithm needs to
scan the whole file looking for breakpoints, which is very slow (about 20MB/s using a single 2GHz core). 
StoreGPU\cite{storegpu08}
exploits the possibility of using GPU to chunk the file,
their results are exciting. Another option is to use parallel
chunking algorithm to improve the chunking speed,
so that future's many-core chips will be helpful. 
Meanwhile, stripping files is not a quite big issue in cloud storage scenario,
because it is expected to be done at the client side before files are
sent to the cloud.

Since content-based chunking strips files into data blocks 
and identify them by content hash,
it is very natural to build CAS system base on it.
Jumbo Store and others\cite{jumbo07,efficient_dedup05,you06} encodes directory tree snapshots
into a graph whose nodes are data blocks and edges
are hash value pointers.
Directory metadata, file metadata and data chunk are all
represented in the form of variable-size data blocks that identified by content hash.
A object which encapsulate metadata also has a list of hash identifiers 
that point to other blocks it contains.
Such a de-duplication storage system has some great advantages 
in terms of space efficiency, file transmission efficiency (through a LBFS-like protocol), 
and data integrity checking (by verifying the hash).

Cumulus\cite{cumulus09} is a client side backup tool to store 
file system snapshots in exist cloud storage such as S3.
To create a snapshot, Cumulus uses content-based chunking to break files into data blocks,
then compare (by hash) them to the list of stored blocks (in local logs).
New blocks will be packed and compressed into a segment file, and sent to server.
The advantage of Cumulus is portability, because it makes 
the de-duplication backup totally opaque to the server.
However, without the de-duplication support from protocol and server side, 
it's hard to have efficient storage management, and from server's perspective,
snapshots from many users still contain much redundant data.

@@

\section{Architecture Options} 
\label{back:arch}
The way that backup storage architecture envolves has been following the pace of
primary storage, so we will give a glimpse on primary storage's evolution first.
Organizations start with building their virtualization infrastructure using the
traditional servers-connected-to-storage-over-a-network architecture, which
can’t adapt to the ever-changing demands of virtualization. In addition to slow
performance, network storage has become the single biggest source of cost and
complexity in virtualized environments. The network storage-based architecture
worked well for physical servers that served relatively static workloads.
Virtualization, and now Cloud Computing, has made data centers extremely
dynamic\cite{berkeleycloud09}; virtual machines are created on the fly, move from server to server and
depend heavily on shared resources. These characteristics make the management
of virtual machines and their underlying physical infrastructure extremely
complex: Data volumes are growing at a rapid pace in the data center, thanks to the ease
of creating new VMs. In the enterprise, new initiatives like desktop virtualization
contribute to this trend. Service providers deal with an even larger number of
VMs as they build data centers to serve customers who can’t afford the cost
and management overhead that virtualization requires. This growing pool of
VMs is exerting tremendous cost, performance and manageability pressure on
the traditional architecture that connects compute to storage over a multi-hop
network.

@@

In cooperate with the changes of primary storage in cloud, backup storage architecture
has to envolve as well. A dedicated backup storage appliance sits aside the cloud does provide some good properties,
such like it deduplicates all the backup data together so it provides good deduplication efficiency,
 and because it uses dedicated hardware to fingerprint lookups, it leaves very small resource footprint on the client side.
However, its weakness on high-cost and bandwidth demand make it unsuitable for large scale cloud
backup scenario. This is especially true for public clouds whose users are very sensitive
to the storage pricing.

@@

>>>>

\section{Deduplication}
\label{back:dedup}
Backup storage for VM snapshots in the cloud contains petabytes of data from many VMs,
the data redundancy in such a data set is very high\cite{Jayaram2011, agrawal07}.
If we treat each snapshot as a single data object, the similarities between snapshots
can not be utilized. Therefore we need better method to break files into data blocks.
In the recent decade, data deduplication techniques are emerged to solve this data
redundancy problem in backup systems.
Most of data deduplication methods can be categorized by their granularity:

@@

\item \textbf{By variable size block:} This method breaks data into variable size blocks, and the block boundary
is only decided by local data content, so it is also called content-based chunking.
Because of the chunk boundaries are only decided by local data content,
this method is modification-resistant. It resolves the
limitations in the previous two methods, and provides
best deduplication efficiency.
\end{itemize}

@@

Policroniades\cite{poli04} gives out
experimental results and present a comparative analysis
to three deduplication methods: First, the content based chunking
is always the best strategy to discover redundancy in any data sets.
Second, the fixed size block method can sometimes provides
close results compare to content based chunking, and it brings significant less
overhead to computation and data management. Finally, for I/O intensive primary storage system,
data compression is still the most efficient approach to save disk space,
inline data reduction through deduplication has too much random I/O overhead, making it difficult to
justify the limited space savings in a primary storage system.

Data deduplication is extensively used in saving bandwidth for data synchronization.
The popular rsync\cite{rsync} protocol exploits the similarity of two directory trees
using fixed size blocks deduplication.
LBFS uses content-based chunking to improve the NFS protocol,
it avoids transmitting redundant chunks which already exist at the other side.
But data deduplication has its cost. Content-based chunking algorithm needs to
scan the whole file looking for breakpoints, which is very slow (about 20MB/s using a single 2GHz core). 
StoreGPU\cite{storegpu08}
exploits the possibility of using GPU to chunk the file,
their results are exciting. Another option is to use parallel
chunking algorithm to improve the chunking speed,
so that future's many-core chips will be helpful. 
Meanwhile, stripping files is not a quite big issue in cloud storage scenario,
because it is expected to be done at the client side before files are
sent to the cloud.

Since content-based chunking strips files into data blocks 
and identify them by content hash,
it is very natural to build CAS system base on it.
Jumbo Store and others\cite{jumbo07,efficient_dedup05,you06} encodes directory tree snapshots
into a graph whose nodes are data blocks and edges
are hash value pointers.
Directory metadata, file metadata and data chunk are all
represented in the form of variable-size data blocks that identified by content hash.
A object which encapsulate metadata also has a list of hash identifiers 
that point to other blocks it contains.
Such a deduplication storage system has some great advantages
in terms of space efficiency, file transmission efficiency (through a LBFS-like protocol), 
and data integrity checking (by verifying the hash).

Cumulus\cite{cumulus09} is a client side backup tool to store 
file system snapshots in exist cloud storage such as S3.
To create a snapshot, Cumulus uses content-based chunking to break files into data blocks,
then compare (by hash) them to the list of stored blocks (in local logs).
New blocks will be packed and compressed into a segment file, and sent to server.
The advantage of Cumulus is portability, because it makes 
the deduplication backup totally opaque to the server.
However, without the deduplication support from protocol and server side,
it's hard to have efficient storage management, and from server's perspective,
snapshots from many users still contain much redundant data.

@@

\section{Architecture Options} 
\label{back:arch}
The way that backup storage architecture evolves has been following the pace of
primary storage, so we will give a glimpse on primary storage's evolution first.
Organizations start with building their virtualization infrastructure using the
traditional servers-connected-to-storage-over-a-network architecture, which
can’t adapt to the ever-changing demands of virtualization. In addition to slow
performance, network storage has become the single biggest source of cost and
complexity in virtualized environments. The network storage-based architecture
worked well for physical servers that served relatively static workloads.
Virtualization, and now Cloud Computing, has made data centers extremely
dynamic\cite{berkeleycloud09}; virtual machines are created on the fly, move from server to server and
depend heavily on shared resources. These characteristics make the management
of virtual machines and their underlying physical infrastructure extremely
complex: Data volumes are growing at a rapid pace in the data center, thanks to the ease
of creating new VMs. In the enterprise, new initiatives like desktop virtualization
contribute to this trend. Service providers deal with an even larger number of
VMs as they build data centers to serve customers who can’t afford the cost
and management overhead that virtualization requires. This growing pool of
VMs is exerting tremendous cost, performance and manageability pressure on
the traditional architecture that connects compute to storage over a multi-hop
network.

@@

In cooperate with the changes of primary storage in cloud, backup storage architecture
has to evolve as well. A dedicated backup storage appliance sits aside the cloud does provide some good properties,
such like it deduplicates all the backup data together so it provides good deduplication efficiency,
 and because it uses dedicated hardware to fingerprint lookups, it leaves very small resource footprint on the client side.
However, its weakness on high-cost and bandwidth demand make it unsuitable for large scale cloud
backup scenario. This is especially true for public clouds whose users are very sensitive
to the storage pricing.

@@

% ption in transferring the
% % raw data for backup.
